---
title: "Slobr Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{slobr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r example, eval = FALSE}
library(slobr)

# For this tutorial we will use a demo database that is contained within the package
slobr::run_slobr("demo")

```


The app will open in a browser window.

## Adding flobs to a database

1 - Under 'Table Selection', choose 'Table 1'

```{r echo = FALSE, out.width = '50%'}
knitr::include_graphics(paste0(getwd(), "/figures/tut-1.png"))
```
<br /><br />

2 - Select the cell in the table that you would like to populate with a flob, then click 'write cell'

```{r echo = FALSE, out.width = '110%'}
knitr::include_graphics(paste0(getwd(), "/figures/tut-2.png"))
```
<br /><br />

3 - Choose a file and once slobr has indicated that the upload is complete, click 'write'

```{r echo = FALSE, out.width = '70%'}
knitr::include_graphics(paste0(getwd(), "/figures/tut-3.png"))
```


## Adding a flob column to a database table

In some cases, you may need to add a new column in which to store flobs. Take for example the 'RwsData' table, which does not yet have a flob column.

1 - Click 'other options', then 'add column',

```{r echo = FALSE, out.width = '40%'}
knitr::include_graphics(paste0(getwd(), "/figures/tut-4.png"))
```
<br /><br />

2 - Give the new column a name and click 'add column',

```{r echo = FALSE, out.width = '65%'}
knitr::include_graphics(paste0(getwd(), "/figures/tut-5.png"))
```
<br /><br />

3 - You now have a flob column and can populate it as usual.

```{r echo = FALSE, out.width = '120%'}
knitr::include_graphics(paste0(getwd(), "/figures/tut-6.png"))
```

